\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-08-28 paper/paper.tex
Modify section names
A new title

\if0\blind
{
  \title{\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes}
  \author{Eric Mittman \\
    Department of Statistics, Iowa State University\\
    and \\
    Colin Lewis-Beck \\
    Department of Statistics, Iowa State University}
  \maketitle
} \fi

@@

\subsection{Single Drive-Model Analysis}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, drive-model 14.  The Kaplan-Meier estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours, increases from about 10,000 to 20,000 hours, and then starts to gradually flatten out.  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and theoretical justification to apply the GLFP model.

@@

For models 1-4, different sets of restrictions required different prior specifications, which were assigned as follows:

@@

\section{Stan code for model 4}
\label{sec:stan-code}
{\scriptsize
\begin{verbatim}
functions {
  real sev_logpdf(real y, real mu, real sigma){
    real z;
    z = (y - mu) / sigma;
    return -log(sigma) + z - exp(z);
  }

>>>>

\if0\blind
{
  \title{\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}
  \author{Eric Mittman \\
    Department of Statistics, Iowa State University\\
    and \\
    Colin Lewis-Beck \\
    Department of Statistics, Iowa State University}
  \maketitle
} \fi

@@

\subsection{Analysis of a Single Drive-Model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, drive-model 14.  The Kaplan-Meier estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours, increases from about 10,000 to 20,000 hours, and then starts to gradually flatten out.  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and theoretical justification to apply the GLFP model.

@@

For Models 1-4, different sets of restrictions required different prior specifications, which were assigned as follows:

@@

\section{Stan code for Model 4}
\label{sec:stan-code}
{\scriptsize
\begin{verbatim}
functions {
  real sev_logpdf(real y, real mu, real sigma){
    real z;
    z = (y - mu) / sigma;
    return -log(sigma) + z - exp(z);
  }
